### 2014-06-18 kypchak-morphfest-2014/poster.tex
precision and recall definition fixes
git-svn-id: https://svn.code.sf.net/p/apertium/svn/branches/papers/@54593 72bbbca6-d526-0410-a7d9-f06f51895060

%			\begin{itemize}
%				\item split into 10 equal parts; coverage calculated over each separately; standard deviation of mean calculated
%			\end{itemize}
			%both split into 10 equal parts; coverage calculated over each separately; standard deviation of the mean was calculated\\
			\htwo{Evaluation measures}
			\begin{itemize}
				\item \textbf{Naïve coverage} - percentage of surface forms in a given corpus receiving ≥ 1 analysis%\\(surface forms may have missing analyses)
				\item \textbf{Mean ambiguity} - average number of analyses for each surface form found in analysed corpus
				\item \textbf{Precision} - of a form's analyses, \% correct
				\item \textbf{Recall} - \% of analyses provided by transducer that are correct for a form, by comparing against a gold standard
			\end{itemize}
			%\htwo{Coverage results}\\
			\htwo{Evaluation results}
%\centering
%\vspace{1pt}\hspace{2em}
			%%\begin{centering}
			%{\large
			%\begin{itemize}
			%	\item each corpus split into 10 equal parts; coverage calculated over each separately; st.\ dev.\ of mean calculated
			%\end{itemize}
			\vspace{-0.5em}
\begin{center}
		\scalebox{0.94}{
			\begin{tabular}{llrrr}
				\toprule
				 & \textbf{Corpus} & \textbf{Tokens} & \textbf{Coverage} (\%) & \textbf{Amb.} \\
				\midrule

>>>>

%			\begin{itemize}
%				\item split into 10 equal parts; coverage calculated over each separately; standard deviation of mean calculated
%			\end{itemize}
			%both split into 10 equal parts; coverage calculated over each separately; standard deviation of the mean was calculated\\
			\htwo{Evaluation measures}
			\begin{itemize}
				\item \textbf{Naïve coverage} - percentage of surface forms in a given corpus receiving ≥ 1 analysis%\\(surface forms may have missing analyses)
				\item \textbf{Mean ambiguity} - average number of analyses for each surface form found in analysed corpus
%				Precision is the probability that an analysis provided by the transducer is accurate.
%				Recall is the probability that some correct analysis is among those provided.
				\item \textbf{Precision} - probability that a provided analysis is accurate
				\item \textbf{Recall} - probability that a certain correct analysis is among those provided by the transducer
				%\item \textbf{Precision} - of a form's analyses, \% correct
				%\item \textbf{Recall} - \% of analyses provided by transducer that are correct for a form, by comparing against a gold standard
			\end{itemize}
			%\htwo{Coverage results}\\
			\htwo{Evaluation results}
%\centering
%\vspace{1pt}\hspace{2em}
			%%\begin{centering}
			%{\large
			%\begin{itemize}
			%	\item each corpus split into 10 equal parts; coverage calculated over each separately; st.\ dev.\ of mean calculated
			%\end{itemize}
			\vspace{-0.5em}
\begin{center}
		\scalebox{0.94}{
			\begin{tabular}{llrrr}
				\toprule
				 & \textbf{Corpus} & \textbf{Tokens} & \textbf{Coverage} (\%) & \textbf{Amb.} \\
				\midrule
